**Selective DNA and Protein Isolation from Marine Macrophyte Surfaces**

### 2019-11-25 submission/manuscript.Rmd
NC added to analysis

Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0)[@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommandations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 132; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplsts by mothur were exported, aligned using SILVA incremental aligner (SINA, version 1.6.0) [@Pruesse2012] against the same SILVA SSU Ref NR 99 database (release 132) and imported into ARB (version 6.0.6) [@Ludwig2004] for further phylogentic analysis using the same database. Reference sequences close to imported ones were selected and used to calculate a phylogentic tree using the Maximum Likelihood algorithm RAxML (version 7.0.3) with 1000 tree replicates [@Stamatakis2006]. Imported partial chloroplast sequences were added to the tree using the maximum parsimony criteria and not allowing changes to tree topology. Pipeline data processing and visualizaion was done using R (version 3.6.0) [@RCoreTeam2019], package tidyverse (version 1.2.1) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Zhu2019; @Allaire2019; @Xie2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (?????). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was detemined that is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences.

>>>>

Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommandations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 132; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplsts by mothur were exported, aligned using SILVA incremental aligner (SINA, version 1.6.0) [@Pruesse2012] against the same SILVA SSU Ref NR 99 database (release 132) and imported into ARB (version 6.0.6) [@Ludwig2004] for further phylogentic analysis using the same database. Reference sequences close to imported ones were selected and used to calculate a phylogentic tree using the Maximum Likelihood algorithm RAxML (version 7.0.3) with 1000 tree replicates [@Stamatakis2006]. Imported partial chloroplast sequences were added to the tree using the maximum parsimony criteria and not allowing changes to tree topology. Pipeline data processing and visualizaion was done using R (version 3.6.0) [@RCoreTeam2019], package tidyverse (version 1.2.1) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Zhu2019; @Allaire2019; @Xie2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (?????). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was detemined that is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences.
